Parsing Postfix log files

### 2007-09-25 doc/logparser.tex
Critique of splunk.

    \item [Splunk] XXX INVESTIGATE FURTHER \url{http://www.splunk.com}

>>>>

    \item [Splunk] \textit{Splunk is an IT Search engine. It is software
        that indexes any format of IT data from any source in real time,
        including logs, configurations, scripts, code, messages, traps,
        alerts, activity reports, stack traces and metrics from all of your
        applications, servers and devices. Splunk lets you search,
        navigate, alert and report on all your IT data in real time using
        an AJAX web interface. You can also share knowledge and Splunk
        solutions with other members of the Splunk community via
        SplunkBase.\/}

        Splunk aims to index all an organisation's logs, providing a
        centralised view capable of searching and correlating diverse log
        sources.  The web interface allows complicated searches, providing
        statistics and graphs in real time.  Saved searches can be
        configured to run periodically and the results emailed to a
        recipient or sent to a shell script, which presumably can publish
        the results as required (though possibly without the graphs and
        detailed statistics).  In the specific case of parsing Postfix
        logs, Splunk extracts some standard fields: to and from addresses,
        HELO, date, host the logs were collected from, and protocol.  It
        parses the standard syslog fields at the beginning of the line, and
        extracts any \texttt{key=<value>} pairs; these are the fields
        listed above.  Searches can be made based on the extracted fields,
        and all text in the line is also available for searching.  Many
        types of reports are available, though all are variations of a bar
        or pie chart, with the exception of bubble and heatmap graphs.  It
        is very easy to drill down through the graphs to extract a portion
        of the data (e.g.\ select the hour with the largest number of
        events, then select a particular host, and finally a specific
        address).  It is not possible to search on partial words, though
        the web interface does provide and refine a list of possible search
        terms as you type.  The searches are quite fast, though as the free
        version has a limit on the amount of data indexed per day the
        volume of data to be searched was merely 45mb; the cheapest
        licensed version costs \$6000, and it still limits the volume of
        data indexed per day.

        The interface is optimised for interactive rather than automated
        queries and it does not appear to be possible to write independent
        tools to utilise the Splunk database.  Splunk is a generic tool, so
        it lacks any Postfix specific support over and above extracting
        the \texttt{key=<value>} fields; most importantly it makes no
        attempt to correlate log lines by queueid or pid, nor to handle any
        of the myriad complications discussed in this document.
        Correlation of log lines is left up to the user, and Splunk
        certainly makes the job easier than using grep, awk and similar
        Unix tools unless the user has a very high proficiency with those
        tools.

        \url{http://www.splunk.com}
